### 2019-11-26 thesis/txt/0-introduction.tex
describe inter-rater reliability, conclusion and fw, add se logos

CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Build logs are a valuable data source: For developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, for researchers, who can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.

@@

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when trained with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of training examples has no visible influence.
  Fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower precision.
  It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in the accuracy of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, the low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques and program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques: PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.

>>>>

CI builds produce long and verbose build logs~\cite{beller2017oops}, reporting the progress and results of the steps within the build.
The structure of these logs changes from project to project~\cite{staahl2014modeling} as it depends on the tools and the environment used.
Build logs are a valuable data source for developers and researchers.
Developers read them to analyze why their build failed or how different stages of the build process perform.
Researchers can harvest the information contained in the logs to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only use the information within the build logs if they can adequately retrieve the information relevant to them.

@@

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS), and
  \item keyword search (referred to as KWS).
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
How many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and how accurate the retrieved output is(\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when trained with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of training examples has no noticeable influence.
  Fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques, however much lower precision.
  It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in the accuracy of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, its low precision requires a human to interpret the output of the chunk retrieval.

@@

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.

### 2019-11-26 thesis/txt/3-data-set.tex
describe inter-rater reliability, conclusion and fw, add se logos

We manually inspected the collected build logs and had to discard logs from three repositories.
One had only one failed build, two others had empty build logs on Travis CI.
In total we collected 798 \todo{check} logs from 80 repositories.

\todo{image! like in travistorrent paper, /draft 10 mins/}

@@

\section{Data Schema}
For each repository, \emph{LogChunks} has a list of \emph{examples}.
Each example consists of:
\begin{itemize}
	\item \textbf{Input:} the relative path to the input build log.
	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
				The category is relative to the other examples for the same repository.
\end{itemize}
Following, this section describes the BuildFailureReason, Keywords and Category in more detail.
.

@@

\section{Labeling Process}

\paragraph{BuildFailureReason}
For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
They copied out the first continuous description as the BuildFailureReason.
They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.

@@

\subsection{Inter-Rater Reliability Study}
re-labeling of parts of the labels - cohen's kappa
\subsubsection{Introduction}
After the manual labeling of the data set we performed a second labeling of a sample of the build logs to validate the labels.
\subsubsection{Method}
For each label category: Build Failure Reason, keywords and category, we relabeled 30 randomly sampled logs.
compared the labels, \todo{discussed about it}.
\subsubsection{Results}

\subsubsection{Discussion}
main takeaway: overlap yes, but high variation

build failure reason: should we extract the information \emph{that} the build failed as well?
our data set extracts the parts describing \emph{why}, but leaves out the lines stating that the build failed (e.g. step xy exited with 1).

keywords: first labeler allowed also longer strings with spaces and adhered to capitalization.
second one ignored captialization and focussed on the keyword.
so only one word was allowed.
also the first one labeled always a full repository at a time.
so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
second labeler only one build log excerpt (+ context) per repository.
also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')

categories: description for the second labeling stated: sort into categories on why build failed.
was exectued with sorting into test/linter/compilation.
in the case of the selected repositories everything was labeled as test. mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
the categories are thought as structural categories.
so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed

main influence / implication: the labels we select are not black/white. accurate description of what we do is very very important. mainly influenced how we described our data points in the earlier sections.
\subsubsection{Threats to Validity}

\subsection{Developer Survey}
\subsubsection{Introduction}
For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

@@

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds}.

@@

\subsubsection{Discussion}
This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

@@

\subsubsection{Threats to Validity}

>>>>

We manually inspected the collected build logs and had to discard logs from three repositories.
One had only one failed build, two others had empty build logs on Travis CI.
In total we collected 797 logs from 80 repositories.

@@

\section{Data Schema}
\label{sec:data-schema}
For each repository, \emph{LogChunks} has a list of \emph{examples}.
Each example consists of:
\begin{itemize}
	\item \textbf{Input:} the relative path to the input build log.
	\item \textbf{BuildFailureReason:} the substring of the log describing the reason the build failed.
	\item \textbf{Keywords:} keywords a developer would use to search for the BuildFailureReason.
	\item \textbf{Category:} a categorization of the structural representation of the BuildFailureReason within the build log.
				The category is relative to the other examples for the same repository.
\end{itemize}
Following, this section describes the BuildFailureReason, Keywords and Category in more detail.

@@

\section{Labeling Process}
\label{sec:labeling-process}

\paragraph{BuildFailureReason}
For each repository, the labeler skimmed through the build logs and tried to identify the first occurrence of a description why the build failed.
They copied out the first continuous description as the BuildFailureReason.
They preserved whitespace and special characters, as they might be crucial to detect the targeted substring.
To support exact learning of regular expressions identifying the labeled substrings the labeler aimed to start and end the labeled substring at consistent locations around the fault description.

@@

\subsection{Inter-Rater Reliability Study}
To evaluate the validity of our labeled data points we perform a second labeling of a sample from \emph{LogChunks}.

\paragraph{Method}
A second labeler processed 30 random generated logs for each data point in \emph{LogChunks}.
We followed the same labeling process as described in Section \ref{labeling-process}.
For the build failure reason and the keywords, we presented 30 randomly sampled build logs from distinct repositories in \emph{LogChunks}.
As the structural categories are always relative to the other logs from the same repository we randomly sampled 3 repositories and presented all 10 examples within them to the second labeler.

\paragraph{Results}
For the first labeled data point, namely the substring describing why the build failed, the two labelers exactly agreed in six cases.
In 15 cases the second labeler selected more lines than the first one, in five there was partial overlap and in 4 they completely disagreed.

Regarding the keywords the two labelers completely agreed in nine cases and completely disagreed in two cases.
In nine cases there was partial overlap in the keywords of the two labelers, in two the first labeler selected additional keywords compared to the second, while the second labeler labeled additional keywords in seven cases.

When classifying the labeled substrings into structural categories, the two labelers agreed in 26 cases and disagreed in four cases.

\paragraph{Discussion}
The results of this validation study show that there is overlap in the data from the two labelers, however also a high variation.
We mainly attribute this to not specific enough instructions to the second labeler.
There were implicit, inconsistent assumptions both labelers created during their work.
In the following we describe the inconsistent assumptions between both labelers for each data point and the implications on our description of the data classes.

For the first data class, the reason the build failed, it was ambiguous whether the labeled substring should contain the information \emph{that} the build failed.
This concerns statements like \texttt{The build exited with 1}.
The second labeler included such statements, while the first one only focussed on the log parts describing \emph{why} the build failed, e.g. the name of the failing test case.

While labeling the keywords a developer would use to search for the log part describing why the build failed, the first labeler allowed arbitrary, case-sensitive strings.
In contrast to that, the second labeler focussed on actual \emph{words}, delimited by spaces or special characters, while ignoring capitalization.
A second difference was that the first labeler was presented with all substrings from a repository, yielding more general keywords than the second labeler.
Their keywords were in part specific to the failure itself and therefore would not have caught a log part describing a different reason for the build to fail in the test build log.
%so could take into consideration patterns and see what keywords are exception specific and would only retrieve the failure reason if this specific exception occured.
%also: influene of ansi color codes ``merror'' vs. ``error'' first labeler known as ansi color codes, second one counted it into the word (whole word always)
%first was also more inclined to search for a subpart of a word to make it more generalizeable (``failure`` instead of ``failures'')

For the structural categories this validation study showed a high overlap.
In our instructions to the second labeler we did not emphasize the \emph{structural} aspect enough.
They sorted into categories along \emph{why} the build failed, putting failing tests from different test runners into the same category even though the failing tests were presented differently in the log.

% categories: description for the second labeling stated: sort into categories on why build failed.
% was exectued with sorting into test/linter/compilation.
% in the case of the selected repositories everything was labeled as test. mostly correct (one linter), but more importantly no difference was made in which test step failed / how the failed tests were represented.
% the categories are thought as structural categories.
% so the surrounding sturcture and the way a test failure is communicated is important. e.g. if several tests are run then it is important which ones failed

Our main learning from this study is that adequately communicating all decisions and assumptions on how data is labeled is important and difficult.
We reviewed the misunderstandings and incorporated more thorough descriptions of our data classes in Secton \ref{sec:data-schema}.

@@

\subsection{Developer Survey}

\paragraph{Introduction}
For \emph{LogChunks} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason \emph{LogChunks} describes.
\paragraph{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

\paragraph{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g.\ because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds}.

@@

\paragraph{Discussion}
This study highly strengthens the trust in the validity of the extracted build failure reasons in \emph{LogChunks}.
The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

@@

### 2019-11-26 thesis/txt/5-study.tex
describe inter-rater reliability, conclusion and fw, add se logos

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
		\label{fig:failure-reason-categorycount-PBE}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of chunk retrieval with PBE for increasing training set size}
		\label{fig:precision-extraction-result-PBE}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
		\label{fig:recall-precision-examplecount-CTS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training set}
		\label{fig:recall-precision-categorycount-CTS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-CTS}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-KWS}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for all techniques}
		\label{fig:success-partial-all}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
		\caption{Precision and Recall of all techniques compared}
		\label{fig:recall-precision-all}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one} structural category}
		\label{fig:recall-precision-singlecategory-all}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{more than one} structural categories}
		\label{fig:recall-precision-multicategory-all}
\end{figure}

>>>>

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.5\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for increasing number of structural categories in the training set}
		\label{fig:failure-reason-categorycount-PBE}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of chunk retrieval with PBE for increasing training set size}
		\label{fig:precision-extraction-result-PBE}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing training set size}
		\label{fig:recall-precision-examplecount-CTS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing number of structural categories in the training set}
		\label{fig:recall-precision-categorycount-CTS}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-CTS}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.5\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-KWS}
\end{figure}

@@

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for all techniques}
		\label{fig:success-partial-all}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-all.pdf}
		\caption{Precision and Recall of all techniques compared}
		\label{fig:recall-precision-all}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one} structural category}
		\label{fig:recall-precision-singlecategory-all}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{more than one} structural categories}
		\label{fig:recall-precision-multicategory-all}
\end{figure}

### 2019-11-26 thesis/txt/6-discussion.tex
describe inter-rater reliability, conclusion and fw, add se logos

\section{Choosing a Suitable Chunk Retrieval Technique}
This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
It recommends which technique to use depending on the available configuration and 
TABLE!
\paragraph{Configuration and Input}
number of categories:
one? -> pbe
two? -> CTS
more? -> KWS
available examples:
little? -> try pbe (This depends on the categories! here we might want a decision tree to represent the importance of these characteristics against each other? <- this would also anwser RQ1: which ones of the criteria we compare are the most important)
multiple -> kws
very many? -> CTS

\paragraph{Retrieval Output Usage}
precision needed:

\begin{table}[htbp]
\begin{tabular}{|c||c|c|c|}
  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
  \hline
  & one & two & more \\
  PBE & yes & no & no \\ 
  CTS & yes & yes & no \\ 
  KWS & yes & yes & yes \\ 
  \hline
\end{tabular}
\caption{The small $1 \cdot 1$}
\label{tab:101}
\end{table}

\section{Threats to Validity}
chronologically selected examples -> very specific view, devs/users might pick more representative examples

@@

\end{document}

>>>>

\section{Recommendations of Suitable Techniques}
% This section unifies our study results of the chunk retrieval techniques PBE, CTS and KWS\@.
% It recommends which technique to use depending on the available configuration and 
After discussing three chunk retrieval techniques separately we know want to unify out results into one recommendation scheme.
We present a decision tree, which asks questions to a developer or researcher who wants to retrieve information chunks from build logs.
The answers lead the user to more questions or the recommended technique as leaf nodes.
Figure \ref{fig:crt-recommendation} presents the decision tree.

\emph{Caveat!} This is a preliminary theory based on the results from our comparison study.
The recommendations are therefore likely based on our implementation of the chunk retrieval techniques as well as the logs in the LogChunks data set.
This decision tree is the answer to our first research question "which factors influence the suitability of a chunk retrieval technique".
The earlier in the decision tree an aspect is noted, the more important it is in distinguishing the techniques.

First and most important aspect are the structural categories.
Are the textual representations of the BuildLogInformation your would like to extract always presented in the same structural way within the build logs?
Meaning that all training examples are in the same structural category and the expected output in the log the chunk retrieval is applied to as well.

If the textual representations of the BuildLogInformation are from multiple structural categories, meaning the are  not presented in the same structural way within the build logs, and recall is more important than precision we recommend to use KWS.
If the representations are from multiple structural categories and precision is more important than recall to the user we recommend CTS.
We also recommend CTS when the representations are from one structural category, the user does not require a high confidence in the accuracy of the outcome and the user rather have some bad output instead of no output at all.
When the representations are from one structural category and the user wishes a high confidence in the correct need of the output or prefers no output over bad output, we recommend PBE.

\begin{table}[htbp]
\centering
\begin{tabularx}{\textwidth}{@{}llll@{}}
  \toprule
  & PBE & CTS & KWS \\
  \midrule
  Structural Categories & 1 & best if 1 & no influence \\
  Training Set Size & 1 - 3 & no influence & > 2 \\ 
  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
  Output Consumption by & program & human & human \\ 
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques}
\label{tab:single-technique-recommendations}
\end{table}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/crt-recommendation.pdf}
		\caption{Our preliminary recommendation scheme for chunk retrieval techniques}
		\label{fig:crt-recommendation}
\end{figure}

\section{Threats to Validity}

There are several threats to the validity of the conclusions of our work.

\paragraph{Implementation}
Our results are highly dependent on the libraries we used and our implementation of the investigated chunk retrieval techniques.
Our implementation of PBE is mainly based on the program synthesis provided by PROSE.
It's limitations are therefore also mainly influenced by this library.
For example, the need for examples from a single structural category stems from the fact that FlashExtract cannot learn regular expression programs with (too many?) top level OR operators.
This limitation was necessary to keep the synthesis performance reasonable.

Our implementation of CTS is dependent on the information retrieval library tex2vec and the way they split strings into word tokens.
We intentionally chose a simple, minimally configured and tuned approach to compare against.
Of course tuning the text similarity meta parameters more to the specific use case Of build log chunk retrieval or training  examples in specific instances would yield better chunk retrieval results.

\paragraph{Data Set} the outcomes of our comparison study are highly dependent on the build logs from the LogChunks data set.
It only consists of build logs from open source and therefore it is not clear whether our results are generalizable to industry projects.
We only collected build logs from Travis CI, however we chose to evaluate on a BuildLogInformation, the reason the build failed, which format is not dependent on Travis CI.
This is because the reason the build failed is described within the build logs by the tools themselves and not the Travis CI runner.

\paragraph{Training set size}
Especially the results for CTS are influences by the fact that we only trained on one to five examples.
Information retrieval tasks commonly learn on larger data sets. \mention{CITATION NEEDED}
We chose this small training set size as the examples would always have to be provided per repository and we expect a developer to not want to have to provide more examples than the small numbers we evaluated on.

\bp{
chronologically selected examples -> very specific view, devs/users might pick more representative examples

@@

some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed}
\end{document}
